---
title: "Methodology"
subtitle: "Survey design, conditional models, validation and governance"
---

```{r}
#| include: false
source("site/helpers.R")
```

## Estimand

Let $I_i$ indicate a reported internet disruption for connected establishment $i$, $D_i$ its average duration, $L_i$ the reported loss ratio and $w_i$ the survey weight. The primary occurrence estimator is

::: {.formula-box}
$$
\widehat p=\frac{\sum_i w_i I_i}{\sum_i w_i}.
$$
:::

The effective sample size is

$$
n_{\mathrm{eff}}=\frac{\left(\sum_i w_i\right)^2}{\sum_i w_i^2},
$$

which equals `r fmt_num(evidence$effective_n)` for the valid occurrence sample.

## Occurrence GLM

The parsimonious design-weighted model is

$$
I_i\sim\operatorname{Bernoulli}(p_i),
\qquad
\operatorname{logit}(p_i)
=\beta_0+\beta_R^\top R_i+\beta_S^\top S_i+\beta_Z^\top Z_i,
$$

where $R_i$, $S_i$ and $Z_i$ are region, sector and firm-size categories. Coefficients are descriptive risk associations, not causal effects.

## Conditional duration model

For strictly positive duration, the 99th-percentile-capped response is

$$
D_i^*=\min(D_i,Q_{0.99}),
\qquad
D_i^*\mid I_i=1\sim\operatorname{Gamma}(\mu_i,\phi),
\qquad
\log\mu_i=x_i^\top\gamma.
$$

Capping limits the leverage of the single 48-hour response without deleting it.

## Actuarial loss chain

::: {.formula-box}
$$
\widehat{ELR}_{2024}
=\widehat{\Pr}_w(I=1)
\times\widehat{\Pr}_w(L>0\mid I=1)
\times\widehat{\mathbb E}_w[L\mid L>0,I=1].
$$
:::

Numerically,

$$
`r formatC(calibration$disruption_probability, digits = 6, format = "f")`
\times
`r formatC(calibration$positive_loss_probability_given_disruption, digits = 6, format = "f")`
\times
`r formatC(calibration$mean_positive_loss_ratio, digits = 6, format = "f")`
=
`r formatC(calibration$expected_loss_ratio, digits = 7, format = "f")`.
$$

## Weighted resampling uncertainty

Two thousand pseudo-population resamples draw establishment records with replacement using $\pi_i=w_i/\sum_jw_j$. The full three-stage estimator is recomputed in each resample. The percentile interval describes sampling variation under this procedure; it excludes model-form and scenario uncertainty.

## Repeated cross-validation

Internet disruption is available only in 2024, so a temporal holdout would be impossible. Both the GLM and AI challenger use repeated stratified five-fold cross-validation:

$$
\operatorname{BS}_w
=\frac{\sum_{i\in\mathcal V}w_i(I_i-\widehat p_i)^2}{\sum_{i\in\mathcal V}w_i}.
$$

```{r}
#| label: tbl-validation
#| tbl-cap: "Repeated-cross-validation comparison"
metrics <- c("weighted_brier", "prevalence_brier", "weighted_auc", "observed_rate", "predicted_rate")
labels <- c("Weighted Brier", "Prevalence Brier", "Weighted AUC", "Observed rate", "Predicted rate")
display <- data.frame(
  Metric = labels,
  `Actuarial GLM` = unname(formatC(vapply(metrics, function(x) metric_value(validation, x), numeric(1)), digits = 4, format = "f")),
  `Gradient boosting` = unname(formatC(vapply(metrics, function(x) metric_value(ml_validation, x), numeric(1)), digits = 4, format = "f")),
  check.names = FALSE
)
knitr::kable(display, align = c("l", "r", "r"))
```

## Promotion gates

```{r}
#| label: tbl-gates
#| tbl-cap: "Predeclared evidence gates"
display <- data.frame(
  Component = gate$component,
  Evidence = gate$observed_events_or_rows,
  Minimum = gate$minimum_required,
  Decision = ifelse(gate$allowed, "Pass", "Block"),
  check.names = FALSE
)
knitr::kable(display, align = c("l", "r", "r", "c"))
```

The model card records the intended use, validation design, blocked models, public-data boundary and prohibited interpretations.
