---
title: "Network and operator context"
subtitle: "Official QoS campaigns and independent measurement footprint"
---

```{r}
#| include: false
source("site/helpers.R")
```

## Why this layer is separate

WBES measures business experience but does not identify operators. INT measures network quality under defined campaigns but does not observe the surveyed firms' losses. RIPE Atlas observes a volunteer probe footprint. These sources are presented side by side and are never joined at firm level.

## INT fixed-internet benchmark

The official 2020 fixed-internet report evaluated 8 Mbps ADSL access across 24 governorates and five internet service providers. The following values are transcribed from Table 2.

```{r}
#| label: tbl-int-qos
#| tbl-cap: "INT 2020 national fixed-internet QoS benchmark"
display <- data.frame(
  Metric = qos$metric,
  Value = paste(qos$value, qos$unit),
  Assessment = qos$reported_assessment,
  Scope = qos$scope,
  check.names = FALSE
)
knitr::kable(display, align = c("l", "r", "l", "l"))
```

The report's access-availability mean is `r paste0(qos$value[qos$metric == "Access availability"], "%")`. This is a dated campaign statistic, not an estimate of 2024 business disruptions.

## INT mobile campaign coverage

The 2019 mobile data campaign covered 3G/4G measurements in Grand Tunis for Tunisie Télécom, Ooredoo Tunisia and Orange Tunisia. The counts below indicate measurement volume only.

```{r}
#| label: tbl-mobile-scope
#| tbl-cap: "INT 2019 mobile data QoS campaign scope"
display <- data.frame(
  Operator = operator_scope$operator,
  `Measurement attempts` = operator_scope$measurement_attempts,
  Geography = operator_scope$geography,
  Indicators = operator_scope$indicators,
  check.names = FALSE
)
knitr::kable(display, align = c("l", "r", "l", "l"))
```

::: {.callout-note title="No operator ranking from measurement counts"}
More measurement attempts do not mean better or worse service. The project uses the campaign to document that comparable operator-level QoS evidence exists, while respecting its 2019 Grand Tunis scope.
:::

## RIPE Atlas public-probe snapshot

```{r}
#| label: tbl-ripe
#| tbl-cap: "Largest ASN groups in the public Tunisia RIPE Atlas snapshot"
display_data <- head(ripe[order(-ripe$observed_public_probes), ], 10)
display <- data.frame(
  ASN = display_data$asn,
  Holder = display_data$asn_holder,
  Observed = display_data$observed_public_probes,
  Connected = display_data$connected_public_probes,
  check.names = FALSE
)
knitr::kable(display, align = c("r", "l", "r", "r"))
```

RIPE Atlas probes support latency, reachability, DNS and traceroute measurement. The snapshot is a volunteer convenience sample and cannot represent market share, national coverage or operator outage frequency.

## Provenance

Both INT PDFs are downloaded with URL, UTC collection time, byte size and SHA-256 checksum. The complete record is published in [`network_source_manifest.csv`](artifacts/public/network_source_manifest.csv).
